---
title: "Challenge 2: Spicing things up with ggplot2"
author: "Sophia Taylor"
format: html
editor: source
embed-resources: true
code-tools: true
echo: true
self-contained: true
---

For this week's Challenge, you will have three different options to explore.
I've arranged these options in terms of their "spiciness," or the difficulty of 
completing the task. **You are only required to complete one task, but if you are interested in exploring more than one, feel free!**

This is a great place to let your creativity show! Make sure to indicate what
additional touches you added, and provide any online references you used.

# Getting Set-up 

Within this document, make sure to specify that your plots are contained in
your document (`self-contained: true`) and that your code is visible to the reader (`echo: true`). If there are other formatting specifics
you would like to include, feel free to toss those in the YAML, too!

Next, create a setup code chunk to load the packages and read in the
`surveys.csv` data file exactly how you did in Lab 2.

```{r}
library(tidyverse)
library(here)
surveys <- read_csv(here("data", "surveys.csv"))
```

Finally, create another code chunk and paste in your code from Question 14 or Question 15 in Lab 2 -- we will be modifying the box plot of weights by species!

```{r}
ggplot(surveys, aes(x = species, y = weight)) + geom_boxplot(outliers = FALSE) + geom_jitter(color = "orange3", alpha = 0.2) + labs(x = "Species", y = "Weight (grams)") + theme(axis.text.x = element_text(angle = 45))
```


# Medium: Ridge Plots

In Lab 2, you used side-by-side **boxplots** to visualize the distribution of 
weight within each species of rodent. Boxplots have [substantial flaws](https://www.data-to-viz.com/caveat/boxplot.html), namely that they
disguise distributions with multiple modes.

A "superior" alternative is the density plot. However, `ggplot2` does not allow
for side-by-side density plots using `geom_density()`. Instead, we will need to
make use of the `ggridges` package to create side-by-side density (ridge) plots.

> **For this challenge you are to change your boxplots to ridge plots. You will need to install the `ggridges` package and explore the `geom_density_ridges()` function.**

```{r}
library(ggridges)
```

```{r}
ggplot(surveys, aes(x = weight, y = species)) + geom_density_ridges(alpha = 0.5) + geom_boxplot(outliers = FALSE) + labs(x = "Weight (grams)", y = "Species") + theme(axis.text.x = element_text(angle = 45))
```
I read this for more information on the function : https://www.rdocumentation.org/packages/ggridges/versions/0.5.6/topics/geom_density_ridges

# Challenge 2 Submission

Once you have completed your challenge(s) you should upload your rendered HTML file to Canvas.

Your Challenge 2 file **must** be separate from your Lab 2 file. Yes, some of the code for the Challenge is the same as Lab 2 -- you can copy and paste this code into a **new** Quarto file. Your Challenge 2 submission should only included code necessary for completing the Challenge, nothing else.

Similar to Lab 2, you should submit **only** your HTML file. Your HTML file is required to have the following specifications in the YAML options (at the top of your document):

-   have the plots embedded (`embed-resources: true`)
-   include your source code (`code-tools: true`)
-   include all your code and output (`echo: true`)

**If any of the options are not included, your assignment will receive an "Incomplete" and you will be required to submit a revision.**

In addition, your document should not have any warnings or messages output in your HTML document. **If your HTML contains warnings or messages, you will receive an "Incomplete" for document formatting and you will be required to submit a revision.**

